\Large Last Writer Slices and Communication Traps

### 2013-11-05 paper.tex
committing before pushing to dbox and printing.

\paragraph{HTTrack}
The running example in Figures~\ref{fig:coreDumpFail} and ~\ref{fig:httlws},
and the text in Section~\ref{sec:httdebug} describes the benefit provided by
last writer slices in debugging an ordering violation in HTTrack-3.43.9.

@@

We triggered the bug by running an insert query during a log rotation.  The bug
manifested, stopping execution at point {\bf C}.  As described in the bug
report, the query went unlogged and examining the core dump revealed the log
was marked closed at point {\bf B}.  However, the core dump did not reveal {\em
why} the log was marked closed there.  Looking at the last writer slice for the
{\tt log\_type} variable shows that it was written last Thread 1 at {\bf A}.
Seeing here that {\tt log\_type} is accessed by multiple threads
suggests adding synchronization to prevent this atomicity violation.

>>>>

\paragraph{HTTrack}
The running example in Figures~\ref{fig:coreDumpFail} and ~\ref{fig:httlws},
and the text in Section~\ref{sec:debugging} describes the benefit provided by
last writer slices in debugging an ordering violation in HTTrack-3.43.9.

@@

We triggered the bug by running an insert query during a log rotation.  The bug
manifested, stopping execution at point {\bf C}.  As described in the bug
report, the query went unlogged and examining the core dump revealed the log
was marked closed at point {\bf B}.  However, the core dump did not reveal {\em
why} the log was marked closed there.  Looking at the last writer slice for the
{\tt log\_type} variable shows that it was written last Thread 1 at {\bf A}.
Seeing that {\tt log\_type} is accessed concurrently in inserts and
log rotations shows where synchronization needs to be added to fix the bug.
